Applying the metallicity-dependent binary fraction to double white dwarf formation: \\ Implications for LISA

### 2021-10-20 src/ms.tex
we have a working draft!!!!

\acknowledgments
The authors are grateful for helpful discussions with Carles Badenes, Christine Mazzola Daher, and the Gravitational Waves and Astronomical Data groups at the CCA.  S.T.\ was supported by an Undergraduate Student Research Award (USRA) at CITA from the Natural Sciences and Engineering Research Council of Canada (NSERC), Reference \# 498223. K.B.\ is grateful for support from the Jeffrey L. Bishop Fellowship. The Flatiron Institute is supported by the Simons Foundation.

@@

\bibliographystyle{aasjournal}
\bibliography{main}{}

>>>>

\begin{acknowledgments}
The authors are grateful for helpful discussions with Carles Badenes, Christine Mazzola Daher, and the Gravitational Waves and Astronomical Data groups at the CCA.  S.T.\ was supported by an Undergraduate Student Research Award (USRA) at CITA from the Natural Sciences and Engineering Research Council of Canada (NSERC), Reference \# 498223. K.B.\ is grateful for support from the Jeffrey L. Bishop Fellowship. The Flatiron Institute is supported by the Simons Foundation.
\end{acknowledgments}

@@

\bibliographystyle{aasjournal}
\bibliography{bib}{}
